% -*- root: ../ProjectPlan.tex -*-

\begin{requirement}{Fault's location}
\reqdesc Get the location of the fault, based on the location of the reporter.
\reqin Two kind of external inputs are necessary for determine location:
\begin{itemize}
\item Faculty where the fault is located, given by.
\subitem GPS coordinates (if possible).
\subitem Manually chose location.
\item Manually chose floor and room inside the building where the fault is located.
\end{itemize}
\reqsteps Transform input information into Location object.
\reqout Location object.
\end{requirement}

\begin{requirement}{Incidences report}
\reqdesc The system must allow users to report incidences.
\reqin 
\begin{itemize}
	\item Compulsory external inputs:
	\subitem Title.
	\subitem Category.
	\item Compulsory internal inputs:
	\subitem Location object.
	\item Optional external inputs:
	\subitem Description of the problem.
	\subitem Picture from gallery or taken on the fly (Optional).
\end{itemize}
\reqsteps The system saves into faults database a new record with additional information is added such as \textit{priority}.
\reqout
\begin{itemize}
	\item Reported fault object.
	\item Message to the maintenance personnel.
	\item Notification to the reporter saying the report has been processed, including a brief summary so the user knows exactly which report has been processed.
\end{itemize}
\end{requirement}

\begin{requirement}{Notification user when the fault has been solved}
\reqdesc The user will receive a notification when a fault he has reported has been solved.
\reqin
\begin{itemize}
	\item Compulsory internal input:
 	\subitem Reported fault object.
 	\subitem User object with contact information.
 \end{itemize}
\reqout Message to the user saying the fault has been solved successfully, including a brief summary so the user knows exactly which report has been solved.
\end{requirement}

\begin{requirement}{Select fault to check history}
\reqdesc Registered users will be able to list the faults they had report and select one of them.
\reqin Some optional inputs to filter the history by, such as:
\begin{itemize}
	\item External:
	\subitem Text to match with title.
	\subitem Text to match with description.
	\subitem Faults per page.
	\item Internal:
	\subitem Location object.
	\subitem Date.
\end{itemize}
\reqsteps The list will be shown and the user can give interactively values to filter the list.
\reqout 
\begin{itemize}
	\item External Query:
	\subitem A list of reported faults ordered by date, containing as much as the number of faults per page given by the user or using the default value.
\end{itemize}
\end{requirement}

\begin{requirement}{Check history of reported fault}
\reqdesc Registered users will be able to check details of a reported fault.
\reqin Fault reported object with all information attached.
\reqout Report showing all the information attached to the object.
\end{requirement}
