% -*- root: ../ProjectPlan.tex -*-
Estimations of time and complexity of the system are basic in order to make a project plan adjusted to the real development time. On the contrary, we won't have any basis to aproximate that time, depending just on a correct planification guided by previous experiences.

With this aim, the size of the Fault Manager Lite project has been estimated using the Function Points estimation technique. Moreover, we have also estimated the Report System (subsystem of FML) with the COCOMO II tool.

\section{Estimation using function points}
\subsection{Unadjusted Function Points}
After the evaluation of the requirements of the proposed system using the Function Points analysis, we have obtained the data of its estimated complexity. We attach tables with the size of the different subsystems in which the application is divided into, with their corresponding estimations in terms of Function Points. For a more detailed analysis of each of the exposed requirements, see \ref{chapFunctionPoints}.


\subsubsection{Task Management Subsystem}
Table \ref{tbl_TMS_UFP} shows the summary of the unadjusted Function Points calculated for the Task Management Subsystem.
\begin{table}[hbtp]
\centering
\input{../CommonTex/TaskManagementFP.tex}
\caption{Overview of the calculation of the Unadjusted Function Points for the Task Management Subsystem.}
\label{tbl_TMS_UFP}
\end{table}

\subsubsection{Report System Subsystem}
Table \ref{tbl_RSS_UFP} shows the summary of the unadjusted Function Points calculated for the Report System Subsystem.
\begin{table}[hbtp]
\centering
\input{../CommonTex/ReportSystemFP.tex}
\caption{Overview of the calculation of the Unadjusted Function Points for the Report System Subsystem.}
\label{tbl_RSS_UFP}
\end{table}

\subsubsection{Notification and Messaging System Subsystem}
Table \ref{tbl_NMSS_UFP} shows the summary of the unadjusted Function Points calculated for the Notification and Messaging System Subsystem.
\begin{table}[hbtp]
\centering
\input{../CommonTex/NotificationMessagingFP.tex}
\caption{Overview of the calculation of the Unadjusted Function Points for the Notification and Messaging System Subsystem.}
\label{tbl_NMSS_UFP}
\end{table}

\subsubsection{User Management Subsystem}
Table \ref{tbl_UMS_UFP} shows the summary of the unadjusted Function Points calculated for the User Management Subsystem.
\begin{table}[hbtp]
\centering
\input{../CommonTex/UserManagementFP.tex}
\caption{Overview of the calculation of the Unadjusted Function Points for the User Management Subsystem.}
\label{tbl_UMS_UFP}
\end{table}

\subsubsection{Faults History and Statistics Subsystem}
Table \ref{tbl_FHSS_UFP} shows the summary of the unadjusted Function Points calculated for the Faults History and Statistics Subsystem.
\begin{table}[hbtp]
\centering
\input{../CommonTex/FaultHistoryStatisticsFP.tex}
\caption{Overview of the calculation of the Unadjusted Function Points for the Faults History and Statistics Subsystem.}
\label{tbl_FHSS_UFP}
\end{table}

\subsubsection{Global Estimation}
Table \ref{tbl_GLOBAL_UFP} shows the summary of the unadjusted Function Points of the whole system, given by the sum of the unadjusted FP of each subsystem.
\begin{table}[hbtp]
\centering
\input{../CommonTex/FunctionPointsSize.tex}
\caption{Overview of the calculation of the Unadjusted Function Points for the whole system.}
\label{tbl_GLOBAL_UFP}
\end{table}

\emph{The number of Unadjusted Function Points of the system is 186.}


\subsection{Adjusting Factor}
Once the unadjusted Function Points of the project have been calculated, these must be ponderated depending of the technical characteristics of the system. To do this, we have evaluated the 14 adjusting characterístics involved in the Function Points method in order to extract the Adjusting Factor for this system.

Table \ref{tbl_ADJ_FACTOR} shows the summary of the values assigned to the general characteristics of the system.

\begin{table}[hbtp]
\centering
\input{../CommonTex/AdjustingFactor.tex}
\caption{Complexity Factor values.}
\label{tbl_ADJ_FACTOR}
\end{table}

Therefore, the TDI is 45.0. The Adjusting Factor (AF) is calculated applying the corresponding formula:
\emph{AF = (TDI x 0.01) + 0.65 = 1.10}

\emph{The Adjusting Factor of the system is 1.10.}

\subsection{Adjusted Function Points}
Once we have obtained the Unadjusted Function Points, UFP, and the Adjusting Factor, AF, we have that the Adjusted Function Points, AFP, are:
\emph{AFP = UFP x AF}

This way, we have that the AFP of each subsystem, as well as the total AFP for the project are the ones exposed in Table \ref{tbl_GLOBAL_AFP}.

\begin{table}[hbtp]
\centering
\input{../CommonTex/AllSubsystemsFP.tex}
\caption{Adjusted Function Points organized by subsystems.}
\label{tbl_GLOBAL_AFP}
\end{table}


\subsection{Time Estimation}

Taking into account all the elements shown in the tables of the previous section and that every Adjusted Function Point implies an estimated effort of \textbf{1.615 person-day}, then we can estimate the time needed to develop every subsystem, and therefore, the whole system itself.

The next tables show a summary for every subsystem estimated time:

\begin{table}[hbtp]
\centering
\input{../CommonTex/TaskManagementTimeEstimate.tex}
\caption{Estimated size (person-day) for the Task Management subsystem.}
\end{table}

\begin{table}[hbtp]
\centering
\input{../CommonTex/ReportSystemTimeEstimate.tex}
\caption{Estimated size (person-day) for the Report System subsystem.}
\end{table}

\begin{table}[hbtp]
\centering
\input{../CommonTex/NotificationMessagingTimeEstimate.tex}
\caption{Estimated size (person-day) for the Notification Messaging subsystem.}
\end{table}

\begin{table}[hbtp]
\centering
\input{../CommonTex/UserManagementTimeEstimate.tex}
\caption{Estimated size (person-day) for the User Management subsystem.}
\end{table}

\begin{table}[hbtp]
\centering
\input{../CommonTex/FaultHistoryStatisticsTimeEstimate.tex}
\caption{Estimated size (person-day) for the Fault History and Statistics subsystem.}
\end{table}

\begin{table}[hbtp]
\centering
\input{../CommonTex/FunctionPointsTimeEstimate.tex}
\caption{Estimated size (person-day) for the whole FML system.}
\label{tbl_FPEstimation}
\end{table}

Tables \ref{tbl_GLOBAL_UFP} and \ref{tbl_FPEstimation} detail the estimation of the project size and time required for its completion based on the method of function points.

Based on these calculations, the project would consist of approximately 207 adjusted function points. That would translate to 330.429 person-days of development time.

\subsection{Estimation using CoCoMo II method}

\textcolor{red}{TODO: Fix this}

